Fuzzy Extractors for Noisy Sources with More Errors Than Entropy

### 2015-02-06 constantRate/ConstCompFuzzExt-crypto.tex
in the middle of surgery rearranging sections

\begin{table}
\begin{center}
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline
Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-and-obfuscate \\
Cons. \ref{cons:first construction}  & high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-and-fuzzy-extract\\
\hline\end{tabular}
\end{center}
%end centering
\caption{Summary of new constructions.  }
\label{tab:upper bounds}
\end{table}

@@

In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.  An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key. \lnote{move this somewhere that makes more sense, probably above where we talk about a ball around a $w'$ and the obvious impossibility}%  A meaningful restriction of correctable errors is an open problem.

@@

\section{Supporting more errors than entropy}
\label{sec:info theory cons}
In this section we show an information-theoretic fuzzy extractor that supports more errors than entropy.
%Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
The construction first condenses entropy from each block of the source and then applies a different fuzzy extractor to the condensed blocks. We'll denote the fuzzy extractor on the smaller alphabet as $(\gen', \rep')$.  A condenser is like a randomness extractor but the output is allowed to be slightly entropy deficient.  Condensers are known with smaller entropy loss than possible for randomness extractors~(e.g.~\cite{dodis2014key}).
\begin{definition}
\label{def:conductor}
A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
\end{definition}

\section{Adding reusability}
\label{sec:sampling}
In the previous section, we showed it was possible to construct a fuzzy extractor for a family of distributions with more errors than entropy.  Using computational techniques we are able to retain many of the advantages of \consref{cons:info theoretic} and achieve a reusable fuzzy extractor.

The construction samples a random subset of blocks $W_{j_1},..., W_{j_\eta}$ and obfuscates the concatenation of these blocks.  Denote this concatenated value by $V_1$.  This process is repeated to produce $V_1,..., V_\ell$ where at least one $V_i$ should be correct to ``unlock'' the correct key.
Let $\sample_{\gamma, \eta}(\cdot)$ be an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.

@@

\noindent
%There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
%\begin{itemize}
%\item Multiple blocks are concatenated together.  This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
%\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.  This requires the use of digital lockers in place of point obfuscations.  Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.  \consref{cons:first construction} only hid part of the key in each obfuscation.  This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
%\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.  This construction works for an arbitrary size alphabet.  We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
%\end{itemize}
The use of a computational primitive~(obfuscation of digital lockers) allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$, as opposed to the information-theoretic setting, where it would be necessary to argue about the entropy of the joint variable $V$.  This is the property that allows reusability.

This construction uses a na\"{i}ve sampler that takes truly random samples, but the public randomness may be substantially decreased by using more sophisticated samplers. (See Goldreich~\cite{goldreich2011sample} for an introduction to samplers.)

@@

\section{Allowing Correlated Symbols}
\label{sec:cor construction}
In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.  Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of the output.

@@

@@

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,  ... , W_\gamma$ be a source in which all blocks $W_j$  are mutually independent.  Let $\alpha$ be a parameter.  Let $J\subset \{1,..., \gamma\}$ be a set of indices such that for all $j\in J$, $\Hoo(W_j ) =\alpha $.  Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \gamma - |J|)$-unguessable block source.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \gamma - |J|)$-unguessable block source.
\end{claim}
\begin{proof}
It suffices to show that for all $j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
We can ignore queries for all blocks but the $j$th, as the blocks are independent. Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic ($S$ can calculate the best coins). Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block. Each $A_k$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed). Thus, the total number of possible responses is $q+1$. Thus, we have the following,
\begin{align*}
\Hav(W_j | View(S^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_j| A_1, \dots, A_q)\\
&=\Hoo(W_j) - |A_1, \dots, A_q|\\
&=\alpha - \log (q+1)\,,
\end{align*}
where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.

@@

Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))> \epsilon_{sec}$.
Let $D$ be such a distinguisher of size at most $s_{sec}$.  That is,
\[
| \expe[D(R, P)] - \expe[D(U, P)] > \epsilon_{sec} = 1/\poly(n).
\]
Define the oracle $I_{v_1, ..., v_\ell, r}(\cdot, \cdot)$ as follows:
\[I_{v_1,..., v_\ell, r}(x, i) =
\begin{cases}
r & v_i = x\\
\perp & \text{otherwise.}
\end{cases}\]
By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
\end{align}
We now prove $S$ cannot distinguish between $R$ and $U$.
\begin{lemma}
\label{lem:sim cannot distinguish samp}
$\Delta(S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}$.
\end{lemma}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline
Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
Cons. \ref{cons:first construction}  & high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\hline\end{tabular}
\end{center}
%end centering
\caption{Summary of new constructions.  }
\label{tab:upper bounds}
\end{table}

@@

%In this work we restrict the distribution of the original reading $w$ and allow $w'$ to be an arbitrary point within distance $t$.  An alternative approach is to restrict the set of $w'$ where $\gen$ produces the correct key. \lnote{move this somewhere that makes more sense, probably above where we talk about a ball around a $w'$ and the obvious impossibility}%  A meaningful restriction of correctable errors is an open problem. 
%\fi

@@

\section{Reusable Construction for Sources with High-Entropy Samples}
\label{sec:sampling}
Let $w$ be a string of symbols (over an arbitrary alphabet) $w=w_1\dots w_\gamma$. The construction first chooses a random fuzzy extractor output $r$. It then samples a random subset of blocks $v_1=w_{j_1},..., w_{j_\eta}$ and creates a digital locker that hides $r$ using $v_1$.  This process is repeated to produce $\ell$ digital lockers all containing $r$,  each unlockable with $v_1,..., v_\ell$, respectively. Let $\sample_{\gamma, \eta}(\cdot)$ denote an algorithm that  outputs a random subset of $\{1,..., \gamma\}$ of size $\eta$ given let $r_{sam}$ bits of randomness.

@@

\noindent
%There are three main differences between this construction and \consref{cons:first construction}.  They are as follows:
%\begin{itemize}
%\item Multiple blocks are concatenated together.  This comes at a cost to error tolerance but allows us to significant decrease the required entropy in each block.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.
%\item Instead of encoding a bit of the key with each obfuscated value we encode the entire key with each obfuscated value.  This requires the use of digital lockers in place of point obfuscations.  Instead of having to open ``most'' of the obfuscations, it is only necessary for us to open a single obfuscation.  \consref{cons:first construction} only hid part of the key in each obfuscation.  This allowed some blocks in the distribution to be ``weak.''  However, sampling smoothes out $W$ so that all $V_i$ are ``good'' simultaneously.
%\item \consref{cons:first construction} required a large alphabet as blocks were individually obfuscated.  This construction works for an arbitrary size alphabet.  We show it supports $\Huse (W)\le 0$ when the alphabet size is super-constant in the security parameter.
%\end{itemize}
The use of the composable digital lockers allows us to sample multiple times, because we need to argue only about individual entropy of $V_i$.  Composability also allows reusability.

This construction can use the na\"{i}ve sampler that takes truly random samples. If desired, public randomness may be substantially decreased by using more sophisticated samplers. (See Goldreich~\cite{goldreich2011sample} for an introduction to samplers.)

@@

\section{Construction for Sources with High-Entropy Marginals}

\label{sec:cor construction}
In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.  Instead of having large parts of the string $w$ unlock $r$, we have individual symbols unlock bits of the output.

@@

\section{Information-Theoretic Construction for Sparse Block Sources}
\label{sec:info theory cons}
In this section we show an information-theoretic fuzzy extractor that supports more errors than entropy for sparse block sources.
%Information-theoretic fuzzy conductors can be converted to fuzzy extractors using a randomness extractor~(using the information-theoretic analogue of \lemref{lem:cond and cext}).
The construction first condenses entropy from each block of the source and then applies a different fuzzy extractor to the condensed blocks. We'll denote the fuzzy extractor on the smaller alphabet as $(\gen', \rep')$.  A condenser is like a randomness extractor but the output is allowed to be slightly entropy deficient.  Condensers are known with smaller entropy loss than possible for randomness extractors~(e.g.~\cite{dodis2014key}).
\begin{definition}
\label{def:conductor}
A function $\cond : \mathcal{Z}\times \zo^d\rightarrow \mathcal{Y}$ is a $(m, \tilde{m}, \epsilon)$-randomness condenser if whenever $\Hoo(W)\ge m$, then there exists a distribution $Y$ with $\Hoo(Y)\ge \tilde{m}$ and $(\cond(W, seed), seed) \approx_\epsilon (Y, seed)$.
\end{definition}

@@

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,  ... , W_\gamma$ be a source in which all blocks $W_j$  are mutually independent.  Let $\alpha$ be a parameter.  Let $J\subset \{1,..., \gamma\}$ be a set of indices such that for all $j\in J$, $\Hoo(W_j ) \ge \alpha $.  Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \gamma - |J|)$-unguessable block source.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \gamma - |J|)$-unguessable block source.
\end{claim}
\begin{proof}
It suffices to show that for all $j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
We can ignore queries for all blocks but the $j$th, as the blocks are independent. Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic ($S$ can calculate the best coins). Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block. Each $A_k$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed). Thus, the total number of possible responses is $q+1$. Thus, we have the following,
\begin{align*}
\Hav(W_j | View(S^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_j| A_1, \dots, A_q)\\
&=\Hoo(W_j) - |A_1, \dots, A_q|\\
&=\alpha - \log (q+1)\,,
\end{align*}
where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.

@@

Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $\delta^{\mathcal{D}_{s_{sec}}}((R, P), (U, P))> \epsilon_{sec}$.
Let $D$ be such a distinguisher of size at most $s_{sec}$.  That is,
\[
| \expe[D(R, P)] - \expe[D(U, P)] > \epsilon_{sec} = 1/\poly(n).
\]
Define the oracle $I_{v_1, ..., v_\ell, r}(\cdot, \cdot)$ as follows:
\[I_{v_1,..., v_\ell, r}(x, i) =
\begin{cases}
r & v_i = x\\
\perp & \text{otherwise.}
\end{cases}\]
By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $g$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(R, P_1,..., P_\ell)] - \expe [S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
\end{align}
We now prove $S$ cannot distinguish between $R$ and $U$.
\begin{lemma}
\label{lem:sim cannot distinguish samp}
$\Delta(S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(R, 1^{\ell \log |Z|}), S^{I_{v_1, ..., v_\ell, r}(\cdot, \cdot)}(U, 1^{\ell \log |Z|})) \le \ell 2^{-\alpha''}$.
\end{lemma}
